Using DIT to simplify the DBF feasibility test

### 2013-07-19 dit-paper.tex
minor changes

@@

As the synchronous arrival pattern is known to be the worst case, in that particular case we can only consider the interval $[0, t]$. In an asynchronous arrival pattern, it is sufficient to check only intervals where $t_1 < O_{max} + H$, as the values will be periodic after it.\\

In the sequel a closed form expression of the DBF is given in the synchronous case. Intuitively, in that case, it will be a step-function whose increase will occur at every job deadline, with the increase being equal to the execution time of the corresponding job.\\

>>>>

\begin{definition}
	A system is \textbf{synchronous} if all its tasks have no offset, and
	\textbf{asynchronous} otherwise.
\end{definition}

@@

As the synchronous arrival pattern is known to be the worst case
\cite{liu1973scheduling}, in that particular case we can only consider the
interval $[0, t]$. In an asynchronous arrival pattern, it is sufficient to check
only intervals where $t_2 < O_{max} + 2H$, as the system will be
periodic starting from $O_{max} + H$ or sooner \cite{leung1982complexity}.\\

In the sequel a closed form expression of the DBF is given in the synchronous
case. Intuitively, in this case it will be a step-function whose increases will
occur at every job deadline, with the increase being equal to the execution time of the corresponding job.\\
